|

### 2019-12-19 article/letter.tex
revision main text

---
title:
author:
date:
fontsize: 12pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: no
    keep_tex: no
    toc: no
    toc_depth: 3
    template: article-template.latex
---

```{r, message=FALSE, warning=FALSE, echo=FALSE}
# If you need to install any package while knitting the document
r <- getOption("repos")
r["CRAN"] <- "https://cran.rstudio.com/"
options(repos = r)
if (!require("kableExtra")) {
    install.packages("kableExtra")
}
```

\noindent Research & Politics

@@

\noindent We would like to thank you for the opportunity to revise our
manuscript, "Bottom-Up Accountability and Public Service Provision: Evidence
from a Field Experiment in Brazil" (Manuscript ID RAP-19-0144). We have made
many revisions to the paper along the lines suggested by the editor and the
anonymous reviewer and we believe the manuscript has improved significantly as
a result.

We have worked specially hard to clarify the connection between information
provision and mobilisation, a point emphasised by both the editor and the
reviewer. Our efforts in that regard include, first, a new section in the SI
Appendix with a detailed description of _Tá de Pé_'s functionalities and the
associated Facebook campaigns. We explain the precautions we have taken to
ensure that we correctly identify the effect of the TDP app on school outcomes.
Second, we provide a thorough discussion of our additional data sources. More
specifically, we show how the Brazilian Ministry of Education collects and
publicises their data and indicate how our experiment uses that information to
evaluate the robustness of our findings. We believe the new sections help give
the results a clearer interpretation and strenghten our main arguments.

@@

\vspace{.5cm} \noindent Sincerely,

\vspace{.5cm} \noindent The Authors

@@

# Editor Comments and Responses

**1)** The editor writes: "_The reviewer confirmed my own sense that the
manuscript and underlying field experiment are interesting, although you will
see that the reviewer suggests many ways the manuscript can be improved.  I am
in full agreement with the reviewer that you need to reflect more deeply about
the theory and evidence for why information provision via the app could be
connected to mobilization, -- otherwise the null result is not interesting.  As
the reviewer notes, the null result could be due to a disconnect between
information provision and action, or due to who selects into downloading the
app._"

\vspace{.5cm} \noindent \textbf{Response:}

@@

# Reviewer 1 Comments and Responses

**1)** Reviewer 1 writes: "_My biggest concern is there is no discussion of the
actual bottom-up accountability that may (or may not) have occurred. [...] The
authors have devised a nice experiment and I believe their design to have been
appropriately administrated. But the design hinges on several critical
mechanisms that go largely undiscussed: not only must information be available
to citizens such that they might participate in local oversight, but said
citizens must 1) access the information and 2) act on said information. This is
mentioned in the Discussion---that perhaps the app was insufficient to spur
collective action---but that also seems like an empirical question the authors
could feasibly address. [...] Once people downloaded the App, did they use
it?_"

\vspace{.5cm} \noindent \textbf{Response:}

@@

>>>>

% !TEX program = XeLaTeX
\documentclass[12pt,a4paper,]{article}

% Fonts
\usepackage{libertine}
% This is a nice mathfont, it fits well with Libertine
% Comment the line if you want to use a different one
\usepackage[libertine]{newtxmath}
% The default monofont 
% Again, comment the line below if you want to change it
\usepackage[scaled=.95]{inconsolata}

% Add the following packages to support kableExtra
\usepackage[normalem]{ulem}
\usepackage{array}
\usepackage{booktabs}
\usepackage{colortbl}
\usepackage{etoolbox}
\usepackage{longtable}
\usepackage{makecell}
\usepackage{multirow}
\usepackage{pdflscape}
\usepackage{subcaption}
\usepackage{tabu}
\usepackage{threeparttablex}
\usepackage{threeparttable}
\usepackage{tocloft}
\usepackage{wrapfig}

% Dots in toc
\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}

% Colours
\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{darkblue}{rgb}{0.0,0.0,0.55}

% Spacing
\usepackage{setspace}

% Margin
\usepackage[margin=2cm]{geometry}

% Packages I've been using for different reasons...
\usepackage{hyperref}
\usepackage{dcolumn}
\usepackage{graphicx}
\usepackage{float}
\floatplacement{figure}{H}
\usepackage{pgf}
\usepackage{mathtools}
\usepackage{caption}

% UK English
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\cleanlookdateon

% Penalties
\exhyphenpenalty=1000
\hyphenpenalty=1000
\widowpenalty=1000
\clubpenalty=1000

% Hypersetup
\hypersetup{
  linkcolor=Mahogany,
  citecolor=Mahogany,
  urlcolor=darkblue, 
  breaklinks=true, 
  colorlinks=true,
      }

% If XeTex, LuaLaTeX, etc
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{amssymb,amsmath}
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}

% Language

% Bibliography
\usepackage{natbib}
\bibliographystyle{apalike}
\makeatletter
% Remove comma after author
\setcitestyle{aysep={}}
\patchcmd{\NAT@citex}
	  {\@citea\NAT@hyper@{%
		 \NAT@nmfmt{\NAT@nm}%
		 \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
		 \NAT@date}}
	  {\@citea\NAT@nmfmt{\NAT@nm}%
	   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}
	\patchcmd{\NAT@citex}
	  {\@citea\NAT@hyper@{%
		 \NAT@nmfmt{\NAT@nm}%
		 \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
		   {\@citeb\@extra@b@citeb}%
		 \NAT@date}}
	  {\@citea\NAT@nmfmt{\NAT@nm}%
	   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
	  {}{}
% Patch case where name and year are separated by aysep
\patchcmd{\NAT@citex}
  {\@citea\NAT@hyper@{%
     \NAT@nmfmt{\NAT@nm}%
     \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
     \NAT@date}}
  {\@citea\NAT@nmfmt{\NAT@nm}%
   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}
% Patch case where name and year are separated by opening bracket
\patchcmd{\NAT@citex}
  {\@citea\NAT@hyper@{%
     \NAT@nmfmt{\NAT@nm}%
     \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
       {\@citeb\@extra@b@citeb}%
     \NAT@date}}
  {\@citea\NAT@nmfmt{\NAT@nm}%
   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
  {}{}
\makeatother

% Listings

% Verbatim

% Tables

% Graphics

% Make links footnotes instead of hotlinks:
%  \setlength{\emergencystretch}{3em}  % prevent overfull lines
 \providecommand{\tightlist}{%
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Numbered sections
\setcounter{secnumdepth}{0}
% % % Redefines (sub)paragraphs to behave more like sections
% \ifx\paragraph\undefined\else
% \let\oldparagraph\paragraph
% \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
% \fi
% \ifx\subparagraph\undefined\else
% \let\oldsubparagraph\subparagraph
% \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
% \fi
% 
% Spacing
\doublespacing

% Title

% Author

% Date
\date{}

% Begin document
\begin{document}

% Abstract

% Table of Contents
\noindent Research \& Politics

@@

\noindent We would like to thank you for the opportunity to revise our
manuscript, ``Bottom-Up Accountability and Public Service Provision:
Evidence from a Field Experiment in Brazil'' (Manuscript ID
RAP-19-0144). We have made many revisions to the paper along the lines
suggested by the editor and the anonymous reviewer and we believe the
manuscript has improved significantly as a result.

We have worked specially hard to clarify the connection between
information provision and mobilisation, a point emphasised by both the
editor and the reviewer. Our efforts in that regard include, first, a
new section in the SI Appendix with a detailed description of \emph{Tá
de Pé}'s functionalities and the associated Facebook campaigns. We
explain the precautions we have taken to ensure that we correctly
identify the effect of the TDP app on school outcomes. Second, we
provide a thorough discussion of our additional data sources. More
specifically, we show how the Brazilian Ministry of Education collects
and publicises their data and indicate how our experiment uses that
information to evaluate the robustness of our findings. We believe the
new sections help give the results a clearer interpretation and
strenghten our main arguments.

@@

\noindent Sincerely,

\noindent The Authors

@@

\hypertarget{editor-comments-and-responses}{%
\section{Editor Comments and
Responses}\label{editor-comments-and-responses}}

\textbf{1)} The editor writes: ``\emph{The reviewer confirmed my own
sense that the manuscript and underlying field experiment are
interesting, although you will see that the reviewer suggests many ways
the manuscript can be improved. I am in full agreement with the reviewer
that you need to reflect more deeply about the theory and evidence for
why information provision via the app could be connected to
mobilization, -- otherwise the null result is not interesting. As the
reviewer notes, the null result could be due to a disconnect between
information provision and action, or due to who selects into downloading
the app.}''

\noindent \textbf{Response:}

@@

\hypertarget{reviewer-1-comments-and-responses}{%
\section{Reviewer 1 Comments and
Responses}\label{reviewer-1-comments-and-responses}}

\textbf{1)} Reviewer 1 writes: ``\emph{My biggest concern is there is no
discussion of the actual bottom-up accountability that may (or may not)
have occurred. {[}\ldots{}{]} The authors have devised a nice experiment
and I believe their design to have been appropriately administrated. But
the design hinges on several critical mechanisms that go largely
undiscussed: not only must information be available to citizens such
that they might participate in local oversight, but said citizens must
1) access the information and 2) act on said information. This is
mentioned in the Discussion---that perhaps the app was insufficient to
spur collective action---but that also seems like an empirical question
the authors could feasibly address. {[}\ldots{}{]} Once people
downloaded the App, did they use it?}''

\noindent \textbf{Response:}

@@

% More bibliography
\bibliography{references.bib}

\end{document}
